---
title: "Fossil Fuel Supply-Side Policies"
output: html_document
params: 
    selection: input$country
    data: "country_overview_largeDF"
    data_mbl: "moratoria_bans_limitsDF"
    data_sr: "subsidy_removalDF"
    data_div: "divestmentDF"
    data_oil: "oilDF"
    data_gas: "gasDF"
    data_coal: "coalDF"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE)
```



## `r params$selection`

<p>&nbsp;</p>


#### Global Climate Risk Index (2017):

    `r params$data['cri']`  

#### Country Greenhouse Gas Emissions (CAIT 2016):

    `r params$data['MTCO2e']` MtCO2e 

#### % Global Emissions:

    `r params$data['global_emissions_percent']` %
    
#### % Share of primary energy coming from fossil-fuels (Coal, Gas, & Oil): 

    `r params$data['fossil_fuel_share_energy_2019']` %
 
<p>&nbsp;</p>

## Fossil Fuel Production

```{r echo=FALSE, eval=TRUE, fig.width=10, fig.height=3}
### MAP FUNCTIONS ###
# pkgs
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(ggplot2))

# plot mbl over time
g1 <- params$data_oil %>% ggplot(aes(x = Date, y = Oil.production..TWh., color = Entity)) + 
        geom_line() + geom_point(size = 1, alpha = 0.8) + 
        ylab("TWh") +  xlab("Year") + theme_bw() +
        xlim(c(oil_production_min_date,oil_production_max_date)) + 
        scale_colour_manual(values=c(Coal)) +
        scale_x_date(date_labels = "%Y", limits=c(oil_production_min_date,oil_production_max_date)) +
        ggtitle("Oil Production") + 
        theme(legend.title = element_blank(), legend.position = "", plot.title = element_text(size=12, hjust = 0.5), 
          plot.margin = margin(5, 10, 5, 5))
g1
g2 <- params$data_gas %>% ggplot(aes(x = Date, y = Gas.production..TWh., color = Entity)) + 
        geom_line() + geom_point(size = 1, alpha = 0.8) + 
        ylab("TWh") +  xlab("Year") + theme_bw() +
        xlim(c(gas_production_min_date,gas_production_max_date)) + 
        scale_colour_manual(values=c(Coal)) +
        scale_x_date(date_labels = "%Y", limits=c(gas_production_min_date,gas_production_max_date)) +
        ggtitle("Gas Production") + 
        theme(legend.title = element_blank(), legend.position = "", plot.title = element_text(size=12, hjust = 0.5), 
          plot.margin = margin(5, 10, 5, 5))
g2
 g3 <- params$data_coal %>% ggplot(aes(x = Date, y = Coal.production..TWh., color = Entity)) + 
        geom_line() + geom_point(size = 1, alpha = 0.8) + 
        ylab("TWh") +  xlab("Year") + theme_bw() +
        xlim(c(coal_production_min_date,coal_production_max_date)) + 
        scale_colour_manual(values=c(Coal)) +
        scale_x_date(date_labels = "%Y", limits=c(coal_production_min_date,coal_production_max_date)) +
        ggtitle("Coal Production") + 
        theme(legend.title = element_blank(), legend.position = "", plot.title = element_text(size=12, hjust = 0.5), 
          plot.margin = margin(5, 10, 5, 5))
g3
```
Source: https://ourworldindata.org/fossil-fuels
<p>&nbsp;</p>

## Policies  
<p>&nbsp;</p>

#### Total number of supply-side policies: 
    
    `r sum(params$data['Policy_total'])`
    
#### Moratoria, Bans, Limitations:  

    `r sum(params$data['Moratoria_bans_limits_total'])`
    
#### Subsidy Removals: 

    `r sum(params$data['Subsidy_removal_total'])`
    
#### Number of Divestments: 

    `r sum(params$data['Divestment_total'])`
    
<p>&nbsp;</p>


## Breakdown of policies across sectors and levels 

<p>&nbsp;</p>

### Government Policies

#### Total number of Governmental Policies: 

    `r sum(params$data['Government_policies_total'])`
    
#### National level governmental policies (Subsidy Removal):

    `r sum(params$data['Subsidy_removal'])`
        
#### National level governmental policies (Moratoria, bans, & limits): 

    `r sum(params$data['mbl_country'])`
        
#### State/city governmental level policies (Moratoria, bans, & limits):

    `r sum(params$data['mbl_city_region'])`
        
#### State/city governmental level policies (Divestments):

    `r sum(params$data['divestment_city_region'])`
    
<p>&nbsp;</p>

### Non-Governmental Policies  

#### Total number of non-governmental policies: 

    `r sum(params$data['Non_Government_policies_total'])`

<p>&nbsp;</p>
<p>&nbsp;</p>