---
output: html_document
params: 
    selection: null
    data: null
    data_mbl: null
    data_sr: null
    data_div: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE)
```

```{r echo=FALSE, eval=FALSE}
includeMarkdown(
    rmarkdown::render("report_template.Rmd", params = list(selection = input$country, data = country_overview_largeDF()))
)
```

# **`r params$selection`**

### Overview of policies for `r params$selection`:

#### Total number of supply-side policies: `r sum(params$data['Policy_total'])`
    Moratoria, Bans, Limitations:  `r sum(params$data['Moratoria_bans_limits'])`
    Subsidy Removals: `r sum(params$data['Subsidy_removal'])`
    Number of Divestments: `r sum(params$data['Divestment'])`
                                         
### Breakdown of policies across sectors (government vs. non-government) and levels (country vs. state/city vs. organization): 
#### Government Policies
    Number of All Governmental Policies: `r sum(params$data['Government_policies_total'])`
    Number of national level governmental policies: `r sum(params$data['mbl_country'])`
    Number of state/city governmental level policies (Moratoria, bans, & limits): `r sum(params$data['mbl_city_region'])`
    Number of state/city governmental level policies (Divestments): `r sum(params$data['divestment_city_region'])`

#### Non-Governmental Policies
    Number of non-governmental policies: `r sum(params$data['Non_Government_policies_total'])`
    Number of Divestment policies: `r sum(params$data['divestment_city_region'])`


```{r echo=FALSE, eval=TRUE}
# pkgs
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(kableExtra))

```

```{r echo=FALSE, eval=FALSE}
includeMarkdown(
    rmarkdown::render("report_template.Rmd", params = list(selection = input$country, data_mbl = moratoria_bans_limitsDF()))
)
```




